### 2016-01-20 paper.tex
Add K transport derivation and motivation; resolves #6

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

@@

Weighted averages for the transport terms in the mean kinetic energy
equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport due to
the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though evaluating these trade-offs will
require a detailed analysis of the downstream evolution and turbine--wake
interaction.

>>>>

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\def \p{\partial}
\def \d{\mathrm{d}}
\def \D{\mathrm{D}}

@@

Analysis of the near-wake of the higher solidity UNH-RVAT turbine revealed that
vertical advection was the largest contributer to streamwise recovery
\cite{Bachant2015-JoT}, a trait which is considered an advantage of cross-flow
over axial-flow rotors in arrays \cite{Kinzel2012}. A similar analysis was
undertaken for the RM2, starting with the transport equation for mean kinetic
energy, rearranged to isolate the streamwise partial derivative (indices follow
the Einsteinian convention):
\begin{equation}
    \begin{split}
        \frac{\p K}{\p x}
        =
        \frac{1}{U}
        \bigg{[}
        & - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.}}
        - \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
        % Pressure work:
        - \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
        % Work by viscous forces
        + \frac{\p}{\p x_j} 2 \nu U_i S_{ij}
        % Turbulent transport of K
        - \underbrace{
            \frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
        }_{\text{Turb. trans.}} \\
        % Production of k
        & + 
        \underbrace{
            \overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
        }_{k\text{-prod.}}
        % Mean dissipation
        - 
        \underbrace{
            2 \nu S_{ij}S_{ij}
        }_{\text{Mean diss.}}
        \bigg{]}.
    \end{split}
    \label{eq:K-full}
\end{equation}

Terms that were able to be calculated from the experimental data are those that
do not involve $x$-derivatives, since all wake measurement locations were at a
fixed downstream distance. The available terms are the cross-stream advection
($y$-adv.), vertical advection ($z$-adv.), transport due to turbulent
fluctuations ($y$-turb. and $z$-turb., separated by the direction of the
derivative), production of turbulence kinetic energy ($k$-prod.), and the
dissipation due to the mean velocity gradient (Mean diss.).

Derivatives were computed with a second order central difference scheme for
interior points, and a second order inward-facing scheme for the edges,
identical to \cite{Bachant2015-JoT}. Weighted averages for these computation are
shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding,
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport due to
the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though evaluating these trade-offs will
require a detailed analysis of the downstream evolution and turbine--wake
interaction.
